Differences in Homicide Case Information Indicates Why Justice is Not Served

### 2024-12-13 paper/paper.qmd
Started sampling approach section

### Sampling Approach
The population @datahomicides were interested in were homicide victims in cases 
- what is the population, frame, and sample;
- how is the sample recruited;
- what sampling approach is taken, and what are some of the trade-offs of this; 
- how is non-response handled; - They marked it as "Unknown" or left the field blank.

>>>>

### Sampling Approach
The population @datahomicides were interested in were homicide victims in the US [@citetellingstories]. As defined by @citetellingstories, their sampling frame is homicide victims from the 50 largest US cities. However

- what is the population, frame, and sample;
- how is the sample recruited;
- what sampling approach is taken, and what are some of the trade-offs of this; 
- how is non-response handled; - They marked it as "Unknown" or left the field blank.
